A non-contextual hidden variable model for quantum mechanics

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’ + ‘finalPaperNotes.bib’

Non-multiplicativity has implications to Bohm's HV
model (BHVM), where if the initial conditions are
precisely known the entire trajectory of a
particle (guided by the wavefunction) can be
predicted including the individual outcome of
measurements.  BHVM applied to a single spin-half
particle in a Stern-Gerlach experiment, can
predict opposite results for two measurements of
the same operator.  This observation which is
often used as a demonstration of `contextuality'
in BM, does not even inolve  overlapping sets of
compatible measurements to provide two different
contexts~\cite{HardyCntxBM}.  It turns out that,
if one constructs  a one-one map between an
experiment and an observable (by following a
certain convention), the so-called `contextuality'
can be removed from BHVM.  However, the prediction
map so obtained from observables to measurement
outcomes turns out to be non-multiplicative,
suggesting that non-multiplicativity is a more
suitable explanation of non-classicality
of BHVM.

>>>>

Non-multiplicativity has implications to Bohm's HV
model (BHVM), where if the initial conditions are
precisely known the entire trajectory of a
particle (guided by the wavefunction) can be
predicted including the individual outcome of
measurements.  BHVM applied to a single spin-half
particle in a Stern-Gerlach experiment, can
predict opposite results for two measurements of
the same operator.  This observation which is
often used as a demonstration of `contextuality'
in BM, does not even inolve  overlapping sets of
compatible measurements to provide two different
contexts~\cite{HardyCntxBM}.  It turns out that,
if one constructs  a one-one map between an
experiment and an observable (by following a
certain convention), the so-called ``contextuality''
can be removed from BHVM.  However, the prediction
map so obtained from observables to measurement
outcomes turns out to be non-multiplicative,
suggesting that non-multiplicativity is a more
suitable explanation of non-classicality
of BHVM.
